<!-- README.md is generated from README.Rmd. Please edit that file

library(rmarkdown)
render('README.Rmd', output_format=md_document())

-->
```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "##",
  fig.path = "extra/figures/README-",
  error = TRUE
)
knitr::opts_knit$set(global.par = TRUE)
```
# svgchop - Approximate SVG Elements With Line Segments

## Overview

Parse SVG elements and approximate them with straight line segments.  Only a
small set of SVG syntax and commands are recognized.  The parsing is done with
regex so don't expect it to be robust.  The code is unoptimized and a bit of a
mess as the assumptions made when it only dealt with cubic Bézier curves did not
always apply to elements that were added later.

**This package is experimental, lightly tested, poorly documented, and not
intended for production use**.

Caveats aside, it has worked with some non-trivial SVGs.

```{r echo=FALSE}
par(mai=numeric(4))
```
```{r r-logo, fig.width=5, fig.height=5}
# retrieve and parse, and interpolate
library(svgchop)
paths.raw <- parse_svg('https://www.r-project.org/logo/Rlogo.svg')
paths <- interp_paths(paths.raw, steps=3, normalize=TRUE)

coords <- do.call(
  rbind,
  lapply(
    paths,
    function(x) {
      res <- x[['coords']]
      res[[1]] <- res[[1]] - .5
      res[[2]] <- res[[2]] - .5
      res
    }
) )

# Paths are known to be closed in this case, so abuse that to create sub-paths
subpaths <- lapply(
  paths, function(x) {
    x$coords[attr(x$coords, 'starts'),] <- NA
    x$coords$y <- 1 - x$coords$y  # need to flip y values
    x$coords
} )
# Plot!
plot.new()
invisible(
  Map(
    polypath, subpaths, col=c("#A7A8AD", "#1E64B6"),
    border=NA, rule='evenodd'
) )
```
```{r echo=FALSE, eval=FALSE}
png('~/Downloads/logo-chunky.png', width=1200, height=1200, bg='transparent')
plot.new()
invisible(
  Map(
    polypath, subpaths, col=c("#A7A8AD", "#1E64B6"),
    border=NA, rule='evenodd'
) )
dev.off()
```

## Related

* [svgpathtools](https://github.com/mathandy/svgpathtools).
* [objjob svg](http://objjob.phrogz.net/svg/hierarchy) for
  [`getPointAtLength`](http://phrogz.net/svg/convert_path_to_polygon.xhtml).
* [SVG Path Spec](https://www.w3.org/TR/SVG/paths.html), in particular the [Arc
  Implementation Notes](https://www.w3.org/TR/SVG11/implnote.html#ArcImplementationNotes).
* [Mortoray's post](https://mortoray.com/2017/02/16/rendering-an-svg-elliptical-arc-as-bezier-curves/) on converting arcs to Bézier curves.
* [svg.path](https://github.com/regebro/svg.path).

## Acknowledgments

* R Core for developing and maintaining such a wonderful language.
* [W3C](https://www.w3.org/) for the SVG spec and accompanying documentation,
  and more generally for supporting open web standards.
* [MDN](https://developer.mozilla.org/en-US/) for being a fantastic resource for
  web development.
* Paul Murrell for [`gridBezier`](https://cran.r-project.org/package=gridBezier)
  with which we convert SVG curves into piecewise linear paths.
* Jim Hester, Hadley Wickham, etal. for
  [`xml2`](https://cran.r-project.org/package=xml2), which makes
  it easy to extract properties from SVG (among other things).
* [Mortoray](https://twitter.com/edaqa) for pointing me to the SVG arc
  implementation appendix.
* [Hadley Wickham](https://github.com/hadley/), [Peter
  Danenberg](https://github.com/klutometis), etal. for
  [roxygen2](https://cran.r-project.org/package=roxygen2).
* [Yihui Xie](https://github.com/yihui) for
  [knitr](https://cran.r-project.org/package=knitr) and  [J.J.
  Allaire](https://github.com/jjallaire) etal for
  [rmarkdown](https://cran.r-project.org/package=rmarkdown), and by extension
  John MacFarlane for [pandoc](http://pandoc.org/).
* [Github](https://github.com/), [Travis-CI](https://travis-ci.org/),
  [Codecov](https://codecov.io/), [Vagrant](https://www.vagrantup.com/),
  [Docker](https://www.docker.com/), [Ubuntu](https://www.ubuntu.com/),
  [Brew](https://brew.sh/) for providing infrastructure that greatly simplifies
  open source development.
* [Free Software Foundation](http://fsf.org/) for developing the GPL license and
  promotion of the free software movement.

