<!-- README.md is generated from README.Rmd. Please edit that file

library(rmarkdown)
render('README.Rmd', output_format=md_document())
# render('README.Rmd', output_format=html_vignette())
-->
```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "##",
  fig.path = "extra/figures/README-",
  error = TRUE
)
knitr::opts_knit$set(global.par = TRUE)
```
# svgchop - Approximate SVGs With Line Segments

<!-- badges: start -->
[![R build status](https://github.com/brodieG/svgchop/workflows/R-CMD-check/badge.svg)](https://github.com/brodieG/svgchop/actions)
[![](https://codecov.io/github/brodieG/svgchop/coverage.svg?branch=master)](https://codecov.io/github/brodieG/svgchop?branch=development)
<!-- badges: end -->

## Overview

`svgchop` is a "close-enough" SVG interpreter for R.  It parses and converts SVG
geometry into line segments, and other presentation attributes into easily
useable form.  It implements a significant but incomplete portion of the SVG 1.1
spec in an approximate manner.  While you should not expect the results to be
identical to those produced by a conforming implementation, many SVGs are
approximated closely.

This package is aimed at the narrow niche of those who want to extract SVG
elements as polygons before they are drawn to canvas.  It is experimental, and
follows the old-city design model (start with the village well, add features as
needed, next thing you know you have a mess and you do a half-hearted
[_Haussmannization_][2]).  The API is likely to change with minimal concessions
to backward compatibility.   The code has not been optimized.  It will not make
it onto CRAN except in the unlikely event there is substantial external interest
for that to happen.

## Why?

I wanted to render SVGs in 3D using [`rayrender`][4] and I needed the SVGs as
polygons for that:

<img src=extra/r-3d.png alt="R Logo in 3D!" style='width: 650px;'/>

That's it.  If you find any good use-cases for this package do let me know.

## How?

Just point `svgchop::chop` to an SVG file and it will interpret it:

```{r}
library(svgchop)
svg <- chop(R_logo(), steps=3)
```

You can then use the data to plot the polygons however you wish.  Here we do so
with base plotting functionality:

```{r echo=FALSE}
par(mai=numeric(4))
```
```{r r-logo, fig.width=6, fig.height=4}
ext <- attr(svg, "extents")
plot.new()
plot.window(ext$x, rev(ext$y), asp=1)

xy <- get_xy_coords(svg)
fills <- get_fills(svg)
polypath(xy[[1]], col=fills[[1]], border=NA)
polypath(xy[[2]], col=fills[[2]], border=NA)
```

## Installation

`svgchop` is Github-only:

```{r eval=FALSE}
f.dl <- tempfile()
f.uz <- tempfile()
github.url <- 'https://github.com/brodieG/svgchop/archive/master.zip'
download.file(github.url, f.dl)
unzip(f.dl, exdir=f.uz)
install.packages(file.path(f.uz, 'svgchop-master'), repos=NULL, type='source')
unlink(c(f.dl, f.uz))
```

Or if you have `remotes`:

```{r eval=FALSE}
remotes::install_github("brodieG/svgchop")
```

## Feature Coverage

This package implements:

* All basic elements.
* Paths, including all sub-commands.
* Transforms.
* Clipping.
* CSS and in-line styling.
* Gradients[^gradients].

The implementation does not conform to the standard, but it works reasonably
well across a wide variety of SVGs:

<a href=extra/gallery.png style='text-decoration: none; color: inherit;'>
<img
  src=extra/gallery.png style='width: 650px;'
  alt="diptychs comparing SVGs to their svgchop counterparts"
/>
</a>

Each diptych has a browser-rendered image on the left, and an `svgchop`ped
render purposefully coarsely on the right for effect.

`svgchop` implements a `plot` method which we used for the diptychs above.
There are a few issues in matching the browser output: gradients and filters are
not rendered correclty, and the colors aren't quite right (something in the
bowels of my system is causing `png` to apply a color profile that I can't be
bothered to track down).  Notwithstanding, the point of this package is not to
compete with browsers in rasterizing SVGs.  The `plot` method is provided only
to help verify the SVG interpretation is working correctly.

## Documentation

See `?svgchop::chop`, in particular the examples.

## Related Software

* [Rsvg](https://cran.r-project.org/package=rsvg), a wrapper around the [Librsvg
  Gnome library](https://developer.gnome.org/rsvg/), to rasterize SVGs.
* [string2path](https://github.com/yutannihilation/string2path) for converting
  fonts to polygons.
* [svgpathtools](https://github.com/mathandy/svgpathtools) or a Python SVG
  manipulation library.
* [objjob svg](http://objjob.phrogz.net/svg/hierarchy) for
  [`getPointAtLength`](http://phrogz.net/svg/convert_path_to_polygon.xhtml).
* [SVG Path Spec](https://www.w3.org/TR/SVG/paths.html), in particular the [Arc
  Implementation Notes](https://www.w3.org/TR/SVG11/implnote.html#ArcImplementationNotes).
* [normalize-svg-path](https://github.com/jkroso/normalize-svg-path) npm module
  for converting an SVG path to a pure cubic Bézier path.
* [svg-mesh-3d](https://github.com/mattdesl/svg-mesh-3d) npm module for
  converting paths to meshes.

## Acknowledgments

* R Core for developing and maintaining such a wonderful language.
* [W3C](https://www.w3.org/) for the SVG spec and accompanying documentation,
  and more generally for supporting open web standards.
* Daniel Veillard etal. for [libxml2](http://www.xmlsoft.org/), and Jim Hester,
  Hadley Wickham, etal.  for making it available in R with a nice consistent
  interface via [`xml2`](https://cran.r-project.org/package=xml2), which we use
  to easily manipulate SVG files (among other things).
* Angus Johnson for [clipper](http://angusj.com/delphi/clipper.php), and Adrian
  Baddley etal. for making it available in R via
  [polyclip](https://cran.r-project.org/package=polyclip).  We use `polyclip` to
  implement clip paths.
* [Tyler Morgan Wall][5] for [`rayrender`][4] with which I rendered the logos in
  beautiful path-traced glory.
* [MDN](https://developer.mozilla.org/en-US/) for being a fantastic resource for
  web development.
* [Mortoray](https://twitter.com/edaqa) for pointing me to the SVG arc
  implementation appendix via his [blogpost on the topic][3].
* [Hadley Wickham](https://github.com/hadley/), [Peter
  Danenberg](https://github.com/klutometis), etal. for
  [roxygen2](https://cran.r-project.org/package=roxygen2).
* [Yihui Xie](https://github.com/yihui) for
  [knitr](https://cran.r-project.org/package=knitr) and  [J.J.
  Allaire](https://github.com/jjallaire) etal for
  [rmarkdown](https://cran.r-project.org/package=rmarkdown), and by extension
  John MacFarlane for [pandoc](http://pandoc.org/).
* [Github](https://github.com/), [Travis-CI](https://travis-ci.org/),
  [Codecov](https://codecov.io/), [Vagrant](https://www.vagrantup.com/),
  [Docker](https://www.docker.com/), [Ubuntu](https://www.ubuntu.com/),
  [Brew](https://brew.sh/) for providing infrastructure that greatly simplifies
  open source development.
* [Free Software Foundation](http://fsf.org/) for developing the GPL license and
  promotion of the free software movement.

[1]: https://developer.r-project.org/Blog/public/2020/07/15/new-features-in-the-r-graphics-engine/index.html
[2]: https://en.wikipedia.org/wiki/Haussmann%27s_renovation_of_Paris
[3]: https://mortoray.com/2017/02/16/rendering-an-svg-elliptical-arc-as-bezier-curves/
[4]: https://cran.r-project.org/web/packages/rayrender/index.html
[5]: https://github.com/tylermorganwall/

[^gradients]: Gradients are fully parsed and the data required to render them is
  made available to the user.  The built-in plot method reduces them to a single
  color, but the user is free to use better display devices (e.g. `grid` > 4.0)
  that natively support gradients to render them.


